Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-21 draft/chicago-spatial-covid-draft.tex
Changed wording

Note that the SIR model can be viewed as a generalized chemical reaction
\begin{align*}
	S + I	&\longrightarrow	2 I, \\
	I		&\longrightarrow	R.
\end{align*}
However, these two reactions are not reversible, so we are not able to write the energy-dissipation law for the SIR model \cite{Forster_2013, Wang_2020}.
Indeed, taking $\frac{I_t}{S_t} = - 1 + \frac{\gamma}{\tilde{\beta} S}$ and solving this differential equation gives $I = - S + \frac{\gamma}{\tilde{\beta}} \ln(S) + C$.
Thus,
\begin{equation}
	E(S,I) = S + I - \frac{\gamma}{\tilde{\beta}} \ln(S)
\end{equation}
is a conserved quantity for the system.

>>>>

Note that the ODE model can be viewed as a generalized chemical reaction
\begin{align*}
	S + I	&\longrightarrow	2 I, \\
	I		&\longrightarrow	R.
\end{align*}
However, these two reactions are not reversible, so we are not able to write the energy-dissipation law for the ODE model \cite{Forster_2013, Wang_2020}.
Indeed, taking $\frac{I_t}{S_t} = - 1 + \frac{\gamma}{\tilde{\beta} S}$ and solving this differential equation gives $I = - S + \frac{\gamma}{\tilde{\beta}} \ln(S) + C$.
Thus,
\begin{equation}
	E(S,I) = S + I - \frac{\gamma}{\tilde{\beta}} \ln(S)
\end{equation}
is a conserved quantity for the system.
